\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}

### 2019-11-20 Documentation/DataAppendix_AEJ_Final.tex
final submission

\title{For Online Publication \\ Appendix for ``The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China''}
\author{
  \normalsize{{Ji Qi}} \\
  \normalsize{{Chinese Academy of Environmental Science}}
  \and
  \normalsize{{Xin Tang}}\footnote{Corresponding Author: zjutangxin@gmail.com} \\
  \normalsize{{Wuhan University}} \\
  \normalsize{{International Monetary Fund}}
  \and
  \normalsize{{Xican Xi}} \\
  \normalsize{{Fudan University}}
}
\date{{\today}}

@@

The most important data source that we draw upon in Section \rom{1}.B of the main text is the 2007 \textit{National General Survey of Pollution Sources} (henceforth NGSPS). In this section, we provide a detailed description of the dataset, which is based on the following documents:

%The most important data source that we draw upon in Section \rom{1}.B of the main text is the 2007 \textit{National General Survey of Pollution Sources} (henceforth, NGSPS). Since to the best of our knowledge, the data were not used before in economic studies, we provide a detailed description of the dataset in this section. The content in this section is combined from:
\begin{itemize}
    \item
    \textit{Census Program of the National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查方案)\end{CJK}};
    \item
    \textit{Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.508)]} {\begin{CJK}{GBK}{kai}(全国污染源普查条例[中华人民共和国国务院令第508号])\end{CJK}}.
    \item
    \textit{Technical Specifications Requirements of the First National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查技术规定)\end{CJK}}.
\end{itemize}

For an official introduction to the NGSPS and declassified information at the aggregate level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available.

@@

The NGSPS was a joint effort of multiple national ministries in China. The survey was organized directly by the State Council with data collection and quality control done by specially trained field staff. According to the Regulation on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)], faking data would lead to financial penalties or even lawsuits. The purpose of the NGSPS is to understand the total number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection. The term ``pollution source'' here refers to premises, facilities and equipment which discharge pollutants to environment in the process of production, living or other activities or have adverse impact on environment, as well as other sources that result in pollution.

@@

\textit{Additional Technical Features of the Treatment Technologies.---}We are interested in the following features of these technologies: {processing efficiency, designed processing capacity} and {installation costs}. We proxy the {processing efficiency} using one minus the ratio of {emitted COD} to {generated COD}. The {designed processing capacity} (in tons) and {actual installation costs} are recorded directly in the data. We then calculate the {unit capacity costs} by dividing the installation costs with the processing capacity. We use the unit capacity costs as an indicator of the returns to scale of clean treatment equipment. In Figure \ref{fig:techdiff}, in clockwise order we plot the density functions of processing capacity, installation costs, total value of industrial output and unit capacity cost by technology type. For all panels, log-scale is used in the horizontal axes.
\begin{figure}[htbp]
    \begin{center}
    \includegraphics[width=0.4\textwidth]{./Figures/abate_cap.pdf}%
    \includegraphics[width=0.4\textwidth]{./Figures/abate_inv.pdf} \\
    \includegraphics[width=0.4\textwidth]{./Figures/abate_unit.pdf}
    \includegraphics[width=0.4\textwidth]{./Figures/abate_prod.pdf}
    \caption{Technical Features of Different Treatment Technologies}
    \floatfoot{Source: NGSPS. In all panels, the horizontal axes are in log-scale.}
    \label{fig:techdiff}
    \end{center}
\end{figure}

@@

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{The Effects of Removing Distortions from Polluting Sector Only v.s. From Both Sectors}
%\begin{tabular}{lccccccc}%{p{85pt}>{\centering\arraybackslash}p{50pt}>{\centering\arraybackslash}p{50pt}>{\centering\arraybackslash}p{40pt}}%>{\centering\arraybackslash}p{35pt}}%{lccc}
\begin{tabular}{p{90pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{5pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{40pt}}
    \hline \hline
                         & \multicolumn{3}{c}{Polluting}    & & \multicolumn{3}{c}{Non-polluting} \\
    \cmidrule{2-4} \cmidrule{6-8}
    Statistics                 & Benchmark & (i)      & (ii)      & & Benchmark     & (i)    & (ii) \\
    \midrule
    \textbf{CES $=$ 1.5} \\
    \ \ \ Physical Output      & 100.00    & 129.64   & 134.63    & & 100.00        & 129.90 &  98.03 \\
    \ \ \ Price                & 100.00    & 99.97    & 85.00     & & 100.00        & 100.00 & 102.34 \\
    \ \ \ Revenue              & 100.00    & 129.60   & 114.42    & & 100.00        & 129.90 & 100.32 \\
    \midrule
    \ \ \ \# of Firms          & 100.00    & 42.63    & 46.44     & & 100.00        & 41.88  &  95.38 \\
    \ \ \ Mean Size            & 64.31     & 152.21   & 176.17    & & 51.16         & 123.50 &  49.38 \\
    \midrule
    \ \ \ Pollution            & 100       & 74.69    & 80.05     \\
    \ \ \ Intensity            & 100       & 57.81    & 59.47     \\
    \ \ \ Clean Share          & 56.18     & 83.80    & 73.10     \\
    \midrule
    \textbf{CES $=$ 3.0} \\
    \ \ \ Physical Output      & 100.00    & 129.83   & 160.51    & & 100.00        & 129.89 & 89.45  \\
    \ \ \ Price                & 100.00    & 100.02   & 87.38     & & 100.00        & 100.00 & 100.46 \\
    \ \ \ Revenue              & 100.00    & 129.85   & 140.25    & & 100.00        & 129.88 & 89.86  \\
    \midrule
    \ \ \ \# of Firms          & 100.00    & 41.50    & 48.19     & & 100.00        & 42.30  & 89.24  \\
    \ \ \ Mean Size            & 68.36     & 166.29   & 214.24    & & 50.16         & 119.84 & 46.09  \\
    \midrule
    \ \ \ Pollution            & 100       & 74.69    & 89.61     \\
    \ \ \ Intensity            & 100       & 57.53    & 55.81     \\
    \ \ \ Clean Share          & 56.48     & 84.04    & 74.37     \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Note: All of the values are percentages except for mean size, which is the numbers of workers.}
\end{tablenotes}
\label{tab:aggregates_appen}
\end{threeparttable}
\end{table}

>>>>

\title{For Online Publication \\ Appendix for ``The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China''}
\author{
  \normalsize{{Ji Qi}} \\
  \normalsize{{Chinese Academy of Environmental Science}}
  \and
  \normalsize{{Xin Tang}}\footnote{Please send all correspondence to: zjutangxin@gmail.com} \\
  \normalsize{{Wuhan University}} \\
  \normalsize{{International Monetary Fund}}
  \and
  \normalsize{{Xican Xi}} \\
  \normalsize{{Fudan University}}
}
\date{{\today}}

@@

The most important data source that we draw upon in Section \rom{1}.B of the main text is the 2007 \textit{National General Survey of Pollution Sources} (henceforth NGSPS) [\citet{NGSPS:2007}]. In this section, we provide a detailed description of the dataset, which is based on the following documents:

%The most important data source that we draw upon in Section \rom{1}.B of the main text is the 2007 \textit{National General Survey of Pollution Sources} (henceforth, NGSPS). Since to the best of our knowledge, the data were not used before in economic studies, we provide a detailed description of the dataset in this section. The content in this section is combined from:
\begin{itemize}
    \item
    \textit{Census Program of the National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查方案)\end{CJK}}, issued by \citet{CensusProgram};
    \item
    \textit{The Regulations on National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No.508)]} {\begin{CJK}{GBK}{kai}(全国污染源普查条例[中华人民共和国国务院令第508号])\end{CJK}}, issued by \citet{Decree508};
    \item
    \textit{Technical Specifications Requirements of the First National General Survey of Pollution Sources} {\begin{CJK}{GBK}{kai}(第一次全国污染源普查技术规定)\end{CJK}}, issued by \citet{TechSpec}.
\end{itemize}

For an official introduction to the NGSPS and declassified information at the aggregate level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}) prepared by \citet{DataCollect}, which is publicly available. Besides the NGSPS, we also use two other datasets in preparing this appendix: \textit{China National Economic Census} [\citet{CNEC:2004}] and \textit{Statistics of U.S. Businesses} [\citet{SUSB:2004}].

@@

The NGSPS was a joint effort of multiple national ministries in China. The survey was organized directly by the State Council with data collection and quality control done by specially trained field staff. According to the \citet{Decree508}, faking data would lead to financial penalties or even lawsuits. The purpose of the NGSPS is to understand the total number of pollution sources and their distribution in different industries and regions; to understand the generation, discharge and treatment of major pollutants; to establish records for key pollution sources; to build a pollution source information database and an environmental statistics platform; and to provide basis for formulating policies and plans for economic and social development and environmental protection. The term ``pollution source'' here refers to premises, facilities and equipment which discharge pollutants to environment in the process of production, living or other activities or have adverse impact on environment, as well as other sources that result in pollution.

@@

\textit{Additional Technical Features of the Treatment Technologies.---}We are interested in the following features of these technologies: {processing efficiency, designed processing capacity} and {installation costs}. We proxy the {processing efficiency} using one minus the ratio of {emitted COD} to {generated COD}. The {designed processing capacity} (in tons) and {actual installation costs} are recorded directly in the data. We then calculate the {unit capacity costs} by dividing the installation costs with the processing capacity. We use the unit capacity costs as an indicator of the returns to scale of clean treatment equipment. In Figure \ref{fig:techdiff}, in clockwise order we plot the density functions of processing capacity, installation costs, total value of industrial output and unit capacity cost by technology type. For all panels, log-scale is used in the horizontal axes.
\begin{figure}[t]%[htbp]
    \begin{center}
    \includegraphics[width=0.4\textwidth]{./Figures/abate_cap.pdf}%
    \includegraphics[width=0.4\textwidth]{./Figures/abate_inv.pdf} \\
    \includegraphics[width=0.4\textwidth]{./Figures/abate_unit.pdf}
    \includegraphics[width=0.4\textwidth]{./Figures/abate_prod.pdf}
    \caption{Technical Features of Different Treatment Technologies}
    \floatfoot{Source: NGSPS. In all panels, the horizontal axes are in log-scale.}
    \label{fig:techdiff}
    \end{center}
\end{figure}

@@

\begin{table}[t]
\footnotesize
\centering
\begin{threeparttable}
\caption{The Effects of Removing Distortions from Polluting Sector Only v.s. From Both Sectors}
%\begin{tabular}{lccccccc}%{p{85pt}>{\centering\arraybackslash}p{50pt}>{\centering\arraybackslash}p{50pt}>{\centering\arraybackslash}p{40pt}}%>{\centering\arraybackslash}p{35pt}}%{lccc}
\begin{tabular}{p{90pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt}>{\centering\arraybackslash}p{40pt} >{\centering\arraybackslash}p{5pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{45pt} >{\centering\arraybackslash}p{40pt}}
    \hline \hline
                         & \multicolumn{3}{c}{Polluting}    & & \multicolumn{3}{c}{Non-polluting} \\
    \cmidrule{2-4} \cmidrule{6-8}
    Statistics                 & Benchmark & (i)      & (ii)      & & Benchmark     & (i)    & (ii) \\
    \midrule
    \textbf{CES $=$ 1.5} \\
    \ \ \ Physical Output      & 100.00    & 129.64   & 134.63    & & 100.00        & 129.94 &  98.03 \\
    \ \ \ Price                & 100.00    & 99.97    & 85.00     & & 100.00        & 100.00 & 102.34 \\
    \ \ \ Revenue              & 100.00    & 129.60   & 114.42    & & 100.00        & 129.94 & 100.32 \\
    \midrule
    \ \ \ \# of Firms          & 100.00    & 42.63    & 46.44     & & 100.00        & 41.87  &  95.38 \\
    \ \ \ Mean Size            & 64.31     & 152.21   & 176.17    & & 51.16         & 123.50 &  49.38 \\
    \midrule
    \ \ \ Pollution            & 100       & 74.95    & 80.04     \\
    \ \ \ Intensity            & 100       & 57.81    & 59.45     \\
    \ \ \ Clean Share          & 56.18     & 83.80    & 73.10     \\
    \midrule
    \textbf{CES $=$ 3.0} \\
    \ \ \ Physical Output      & 100.00    & 129.83   & 160.51    & & 100.00        & 129.89 & 89.45  \\
    \ \ \ Price                & 100.00    & 100.02   & 87.38     & & 100.00        & 100.00 & 100.46 \\
    \ \ \ Revenue              & 100.00    & 129.85   & 140.25    & & 100.00        & 129.88 & 89.86  \\
    \midrule
    \ \ \ \# of Firms          & 100.00    & 41.50    & 48.19     & & 100.00        & 42.30  & 89.24  \\
    \ \ \ Mean Size            & 68.36     & 166.29   & 214.24    & & 50.16         & 119.84 & 46.09  \\
    \midrule
    \ \ \ Pollution            & 100       & 74.69    & 89.60     \\
    \ \ \ Intensity            & 100       & 57.53    & 55.82     \\
    \ \ \ Clean Share          & 56.48     & 84.04    & 74.37     \\
    \bottomrule
\end{tabular}
\begin{tablenotes}
     \footnotesize{
     \item[$\dagger$]
     Note: All of the values are percentages except for mean size, which is the numbers of workers.}
\end{tablenotes}
\label{tab:aggregates_appen}
\end{threeparttable}
\end{table}

### 2019-11-20 Documentation/Pollution_Final_AEJ_Template_Ver2.tex
final submission

This study draws upon three major data sources: the 2007 National General Survey of Pollution Sources (NGSPS) of China, the 2004 China National Economic Census (CNEC), and the Statistics of U.S. Businesses (SUSB).

\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China. It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for centralized treatment of pollution. In this study, we focus on the {industrial pollution sources}, which consist of businesses generating pollutants from the 39 manufacturing industries. The survey is organized directly by the State Council with data collection and quality control done by specially trained field staff. According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)]}, faking data would lead to financial penalties or even lawsuits. Therefore, the dataset is administrative in its nature and is subject to less concerns of systematic under-reporting.\footnote{In fact, uniform under-reporting of emissions by small and large firms will not change the basic conclusions of this paper. Our results will be contaminated only if under-reporting by large firms is more severe than that by small firms, which is less likely in most polluting industries since larger firms are usually inspected more carefully. For instance, many large firms in these industries are identified as \textit{key sources}, and therefore are inspected and monitored by the government routinely and carefully, making it harder for them to fake data during this one-time survey.} While we are not aware of other economic studies that use NGSPS, a number of studies in environmental sciences have used this dataset. See, for example, \citet{Niuetal:2016}, \citet{Qietal:2017} and the references therein. A more detailed description of the dataset can be found in Online Appendix A.

>>>>

This study draws upon three major data sources: the 2007 National General Survey of Pollution Sources (NGSPS) of China [\citet{NGSPS:2007}], the 2004 China's National Economic Census [CNEC, \citet{CNEC:2004}], and the Statistics of U.S. Businesses [\citet{SUSB:2004}].

\textit{NGSPS.}---The NGSPS was a joint effort of multiple national ministries in China. It covers all of the pollution units from the agricultural, industrial, and domestic sources, as well as facilities for centralized treatment of pollution. In this study, we focus on the {industrial pollution sources}, which consist of businesses generating pollutants from the 39 manufacturing industries. The survey is organized directly by the State Council with data collection and quality control done by specially trained field staff. %According to the \textit{Regulation on the National General Survey of Pollution Sources [Decree of the State Council of the People's Republic of China (No. 508)]}, faking data would lead to financial penalties or even lawsuits.
According to the \citet{Decree508}, faking data would lead to financial penalties or even lawsuits. Therefore, the dataset is administrative in its nature and is subject to less concerns of systematic under-reporting.\footnote{In fact, uniform under-reporting of emissions by small and large firms will not change the basic conclusions of this paper. Our results will be contaminated only if under-reporting by large firms is more severe than that by small firms, which is less likely in most polluting industries since larger firms are usually inspected more carefully. For instance, many large firms in these industries are identified as \textit{key sources}, and therefore are inspected and monitored by the government routinely and carefully, making it harder for them to fake data during this one-time survey.} While we are not aware of other economic studies that use NGSPS, a number of studies in environmental sciences have used this dataset. See, for example, \citet{Niuetal:2016}, \citet{Qietal:2017} and the references therein. A more detailed description of the dataset can be found in Online Appendix A.

### 2019-11-20 Documentation/Replication_Instruction.tex
final submission

% Citations
\usepackage[authoryear,comma]{natbib}
\renewcommand{\bibfont}{\small}
\setlength{\bibsep}{0em}
\usepackage[%dvipdfmx,%
            bookmarks=true,%
            pdfstartview=FitH,%
            breaklinks=true,%
            colorlinks=true,%
            %allcolors=black,%
            citecolor=blue,
            linkcolor=red,
            pagebackref=true]{hyperref}

@@

We use three datasets in our analysis: The National General Survey of Pollution Sources (NGSPS, \begin{CJK}{GBK}{kai}第一次全国污染源普查\end{CJK}), The National Economic Census (CNEC, \begin{CJK}{GBK}{kai}第一次全国经济普查\end{CJK}) and the Statistics of U.S. Businesses (SUSB).
\begin{itemize}
    \item
    The NGSPS is a confidential dataset housed at the Ministry of Ecology and Environment (MEE henceforth). The dataset is subject to regulation by \textit{The Law of the People's Republic of China on Guarding State Secrets} (\begin{CJK}{GBK}{kai}中华人民共和国保守国家秘密法\end{CJK}) because it contains sensitive information. Please refer to \textit{Regulation on Archiving the National General Survey of Pollution Sources Data} (\textit{State Environmental Protection Administration [2007] No.187}, {\begin{CJK}{GBK}{kai}污染源普查档案管理办法[环发[2007]187号]\end{CJK}}). The data can only be accessed within the MEE as well as institutions under its direct supervision (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部及其直属单位\end{CJK}). Researchers affiliated with these institutions should submit application for access following the internal procedure of the MEE. This is how we access the data.

    Individual researchers not affiliated with the MEE and institutions under its direct supervision need to submit the application through the official portal for requesting Information Access (\begin{CJK}{GBK}{kai} 政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}. The url is retrieved on September 15th, 2019 and may vary in the future. All applications are subject to official approval by the General Office of Ministry of Ecology and Environment (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部办公厅\end{CJK}).

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available. We provide a summary in English in Online Appendix A of our paper.
    \item
    The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University. \\ \rtext{MORE INFORMATION IS NEEDED HERE!!!!!!!!}
    \item
    The SUSB is publicly available from the Census Bureau's dedicated website. The url, retrieved on September 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

In the replication files, we cannot provide micro-level data of the NGSPS and CNEC, due to non-disclosure agreements with the MEE and Fudan University. Therefore, we only post the source code that generates the results. However, to facilitate replication by the readers who have access to the datasets, we post the log files when running the analysis on our computer. More details on the log files are provided at the end of this note.

>>>>

% Citations
\usepackage[authoryear,comma]{natbib}
\renewcommand{\bibfont}{\small}
\setlength{\bibsep}{0em}
\usepackage[%dvipdfmx,%
            bookmarks=true,%
            pdfstartview=FitH,%
            breaklinks=true,%
            colorlinks=true,%
            %allcolors=black,%
            citecolor=blue,
            linkcolor=red,
            urlcolor=black,
            pagebackref=true]{hyperref}

@@

We use three datasets in our analysis: The 2007 National General Survey of Pollution Sources (NGSPS, \begin{CJK}{GBK}{kai}第一次全国污染源普查\end{CJK}), The 2004 National Economic Census (CNEC, \begin{CJK}{GBK}{kai}第一次全国经济普查\end{CJK}) and the 2004 Statistics of U.S. Businesses (SUSB).
\begin{itemize}
    \item
    The NGSPS is a confidential dataset housed at the Ministry of Ecology and Environment (MEE henceforth). The dataset is subject to regulation by \textit{The Law of the People's Republic of China on Guarding State Secrets} (\begin{CJK}{GBK}{kai}中华人民共和国保守国家秘密法\end{CJK}) because it contains sensitive information. Please refer to \textit{Regulation on Archiving the National General Survey of Pollution Sources Data} (\textit{State Environmental Protection Administration [2007] No.187}, {\begin{CJK}{GBK}{kai}污染源普查档案管理办法[环发[2007]187号]]\end{CJK}}). The data can only be accessed within the MEE as well as institutions under its direct supervision (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部及其直属单位\end{CJK}). Researchers affiliated with these institutions should submit application for access following the internal procedure of the MEE. This is how we access the data.

    Individual researchers not affiliated with the MEE and institutions under its direct supervision need to submit the application through the official portal for requesting Information Access (\begin{CJK}{GBK}{kai}政府信息公开\end{CJK}) by the MEE at the following url: \url{http://www.mee.gov.cn/weihu/201706/t20170625_416641.shtml}. The url was retrieved on November 15th, 2019 and may vary in the future. All applications are subject to official approval by the General Office of Ministry of Ecology and Environment (\begin{CJK}{GBK}{kai}中华人民共和国生态环境部办公厅\end{CJK}).

    For an official introduction to the NGSPS and declassified information at the aggregated level, interested readers could refer to the book \textit{Data Collection of the National General Survey of Pollution Sources} (\begin{CJK}{GBK}{kai}《污染源普查数据集》, 中国环境科学出版社, 2011\end{CJK}), which is publicly available. We provide a summary in English in Online Appendix A of our paper. For more information on the NGSPS, please visit the following websites: \url{http://env.people.com.cn/GB/8220/113963/index.html}, or \url{http://www.mee.gov.cn/home/ztbd/rdzl/wrypc/}.\footnote{The latter website was initially dedicated to the first NGSPS starting in 2007. Since the launch of the second NGSPS in 2017, the content of the website has been changed accordingly. However, the two surveys share similar structures.} The urls were retrieved on November 15th, 2019 and may vary in the future.
    \item
    The CNEC was conducted by the National Bureau of Statistics (NBS) of China in 2004, and was designed to cover the entire population of Chinese firms in that year. The firm-level data from the CNEC are not available to the general public and therefore not uploaded as part of our data files. For data access, please contact the NBS of China at \url{wgsjsys@stats.gov.cn}. For more information on the CNEC, please visit the dedicated page maintained by NBS at the following url: \url{http://www.stats.gov.cn/ztjc/zdtjgz/zgjjpc}. The url was retrieved on November 15th, 2019 and may vary in the future.
   % The CNEC is also a confidential dataset belonging to National Bureau of Statistics of China. Many universities and institutions have legal copy of the dataset though. Our copy was obtained from Fudan University. \\ \rtext{MORE INFORMATION IS NEEDED HERE!!!!!!!!}
    \item
    The SUSB is publicly available from the U.S. Census Bureau's dedicated website. The url, retrieved on November 15th, 2019, and subject to possible change in the future, is \url{https://www.census.gov/programs-surveys/susb.html}.
\end{itemize}

We cannot provide confidential micro-level data of the NGSPS and CNEC as part of the replication files. Instead, we post the source code that generates the results. However, to facilitate replication by the readers who have access to the datasets, we post the log files when running the analysis on our computer. More details on the log files are provided at the end of this note.
